### 2019-02-15 Sections/economics_of_the_quantum_internet.tex
Sub val++

Consider taking a single unit of time (i.e we are ignoring cost discounting\index{Cost discounting} over multiple units of time) and dividing it amongst a number of nodes, $n_\mathrm{nodes}$, each with their own scaling function, $f_\mathrm{sc}^{(i)}$. The total classical-equivalent runtime of the computation is additive, given simply by a linear combination of the classical-equivalent processing times of the individual nodes. This yields the relationship for combining scaling functions,
\begin{definition}[Combined scaling functions]\index{Combined computational scaling functions}\label{def:comb_sc_func}
The effective combined computational scaling function, $f_\mathrm{sc}^\mathrm{(joint)}$, of a group of participants, each with their own scaling functions, $f_\mathrm{sc}^{(i)}$, is given by,
\begin{align}
	t_\mathrm{joint} &= \sum_{i=1}^{n_{\mathrm{nodes}}} \beta_i \cdot f_\mathrm{sc}^{(i)}(n_\mathrm{global}) \nonumber \\
	&= f_\mathrm{sc}^\mathrm{(joint)}(n_\mathrm{global}),
\end{align}
where $\beta_i$ characterise the share of processing time allocated to each node, and for normalisation,
\begin{align}
\sum_{i=1}^{n_\mathrm{nodes}} \beta_i = 1.
\end{align}

\end{definition}

@@

@@

Let $L(t)$ be the dollar-value of utilising the network's computing resources for a single unit of time. This is obtained as the return made on the value of the network per FLOP,
\begin{postulate}[Cost of computation]\label{post:cost_comp}
The efficient-market dollar-value of a computation for a single unit of time at time $t$, per FLOP is,
\begin{align}\index{Cost of computation}
	L(t) &= \frac{e^{\gamma_\mathrm{ror}} V(t)}{P(t)} \nonumber\\
	&= \frac{e^{\gamma_\mathrm{ror}} C_0{\gamma_C}^{-t}}{\chi_\mathrm{sc}(N_0 {\gamma_N}^t)}.
\end{align}
\end{postulate}
which implies,
\begin{postulate}[Spot price of computation]\index{Spot price of computation} The present-day (\mbox{$t=0$}) spot price of a computation per FLOP is,
\begin{align}
L(0) = \frac{e^{\gamma_\mathrm{ror}}C_0}{\chi_\mathrm{sc}(N_0)}.	
\end{align}
\end{postulate}
That is, the value of computations simply approximates the return on initial hardware investment, scaled by its initial computational power, as is intuitively expected.

@@

@@

%
% Subjective vs Objective Value of Computation
%

\subsection{Subjective vs. objective value of computation}\index{Subjective value of computation}\index{Objective value of computation}\label{sec:sub_vs_obj}

>>>>

Consider taking a single unit of time (i.e we are ignoring cost discounting\index{Cost discounting} over multiple units of time) and dividing it amongst a number of nodes, $n_\mathrm{nodes}$, each with their own scaling function, $f_\mathrm{sc}^{(i)}$. The total classical-equivalent runtime of the computation is additive, given simply by a linear combination of the classical-equivalent processing times of the individual nodes. This yields the relationship for combining scaling functions,
\begin{definition}[Combined scaling functions]\index{Combined computational scaling functions}\label{def:comb_sc_func}
The effective combined computational scaling function, $f_\mathrm{sc}^\mathrm{(joint)}$, of a group of participants, each with their own scaling functions, $f_\mathrm{sc}^{(i)}$, is given by,
\begin{align}
	t_\mathrm{joint} &= \sum_{i=1}^{n_{\mathrm{nodes}}} \beta_i \cdot f_\mathrm{sc}^{(i)}(n_\mathrm{global}) \nonumber \\
	&= f_\mathrm{sc}^\mathrm{(joint)}(n_\mathrm{global}),
\end{align}
where $\beta_i$ characterise the share of processing time allocated to each node, and for normalisation,
\begin{align}
\sum_{i=1}^{n_\mathrm{nodes}} \beta_i = 1.
\end{align}
\end{definition}

@@

\subsection{Objective value}\index{Objective value of computation}

@@

Let $L(t)$ be the dollar-value of utilising the network's computing resources for a single unit of time. This is obtained as the return made on the value of the network per FLOP,
\begin{postulate}[Objective value of computation]\label{post:cost_comp}
The efficient-market dollar-value of a computation for a single unit of time at time $t$, per FLOP is,
\begin{align}\index{Cost of computation}
	L(t) &= \frac{e^{\gamma_\mathrm{ror}} V(t)}{P(t)} \nonumber\\
	&= \frac{e^{\gamma_\mathrm{ror}} C_0{\gamma_C}^{-t}}{\chi_\mathrm{sc}(N_0 {\gamma_N}^t)}.
\end{align}
\end{postulate}
which implies,
\begin{postulate}[Spot price of computation]\index{Spot price of computation} The present-day (\mbox{$t=0$}) spot price of a computation per FLOP is,
\begin{align}
L(0) = \frac{e^{\gamma_\mathrm{ror}}C_0}{\chi_\mathrm{sc}(N_0)}.	
\end{align}
\end{postulate}
That is, the value of computations simply approximates the return on initial hardware investment, scaled by its initial computational power, as is intuitively expected.

@@

\subsection{Subjective value}\index{Subjective value of computation}

With access to $n$ qubits, let the subjective value extracted by user $i$ from its execution for a unit of time be characterised by $f_\mathrm{sub}^\mathrm{(joint)}(n)$. Then, the joint subjective value of computation (i.e total market subjective return) follows the same form as the joint computational scaling function given in Def.~\ref{def:comb_sc_func},

\begin{definition}[Subjective value of computation]\index{Subjective value of computation}\label{def:sub_val_comp}
The joint subjective value of a time-share in the global network, $f_\mathrm{sub}^\mathrm{(joint)}$, of a group of participants, each with their own subjective valuation functions, $f_\mathrm{sub}^{(i)}$,
\begin{align}
	f_\mathrm{sub}^\mathrm{(joint)} = \sum_{i=1}^{n_{\mathrm{nodes}}} \beta_i \cdot f_\mathrm{sub}^{(i)}(n_\mathrm{global}).
\end{align}
\end{definition}

@@
